Determining Causes of Death with ChatGPT: A Case Study of Verbal Autopsy Data in Sierra Leone from 2019-2022

### 2024-01-10 manuscript/manuscript.tex
Working on methods

\noindent For InterVA5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were transformed into the 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}. The 2016 WHO VA revision 1.5.1 ODK data was further transformed into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}.

>>>>

For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first transformed into the 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}. Then, these transformed data were further transformed into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA.
